A Motion Blur Resilient Fiducial Marker For Quadcopter Imaging

### 2014-03-04 ECCV/paper.tex
Long captions, added figures for BLUT comparison and many more ...

In order to be effective, fiducial markers (or simply, fiducials) need
to be easily detected in the scene.  A variety of fiducial markers
have been proposed in the literature (e.g.~\cite{NaimarkF02,ARToolkit02,Fiala05,Pitag13,runetag11}).
These take the form of binary codes arranged into rectangular grids (\cite{ARToolkit02,Fiala05})
or other geometric features arranged in predefined spatial patterns
(\cite{NaimarkF02,Pitag13,runetag11}).
Figure \ref{fig:teaser}-top shows an example of the popular ARTag\cite{Fiala05} as
seen from a quadcopter.  A problem for existing fiducials is  that low-cost quadcopters
oftenexhibit very quick and erratic physical movements that
results in motion blur in the quadcopters onboard camera.  This motion blur has an adverse effect the  recognition of fiducial  markers.  This can be seen in Figure
\ref{fig:teaser}(top) where the ARTag cannot be recognized due to motion blur. This is not too surprising as most  existing fiducials are not explicitly designed to handle motion blur.

@@

[MSB: related works still needs a couple more passes, I've left it as it.
as mentioned yesterday, we need to address the problems with the circular 
pattern design, this needs to be done in the same paragraph, not later as done now. ]

@@

Most tracking methods( \cite{Ross:2008,Wu:2009,Perez02}
\cite{Mei:2009} ) assume the image sequence to be blur free. In reality, however,
motion blur in video sequences is often unavoidable. Wu et al.\cite{Wu:2011} have
developed BLUr-driven Tracker (BLUT) framework for tracking motion-blurred
targets. BLUT is based on the observation that although motion blurs degrade
the visual features of the target, they at the same time, provide useful cues
about the movements to help tracking.

@@

Before we detail the design of our fiducial, we examine the performance of two
popular fiducials under motion blur.  Specifically we examine ARTags\cite{Fiala05} and PiTags\cite{Pitag13} given their difference in geometry design.

To simulate the appearance of the maker as seen by a quadcopter, 
we scaled down ARTag as well as PiTag fiducial to size 150x150. 
 Both fiducials are then blurred at various orientations with different blurs scales
(denoted in pixels).   The blur motion ranged from X to Y in magnitude, representing
small to significant moton blur.   Figure \ref{fig:artag_pitag} shows the visual appearance
of the blurred tags.   We then use try to detect the markers using the 
ALVAR library\cite{alvar} and Pi-Tag library\cite{ros_pitag}.
The table in the left side of Figure
\ref{fig:artag_pitag} shows the recognition rate (in percent) of two fiducial
markers at various blur scales under different orientation.   As we can see, the PiTag performance quickly diminished under small amounts of blur, however, at 40 motion blur, ARTag is recognition rate drops to less than 20\%.

\begin{minipage}[h!]{\textwidth}
\centering
 \begin{minipage}{0.7\textwidth}
\includegraphics[width=\linewidth]{artag_pitag.pdf}
%\captionof{figure}{Blurred AR Tag and Pi--tag with various blur scales}
\end{minipage}
\begin{minipage}{0.25\textwidth}
%\captionof{table}{Recognition rate of AR Tag and Pi-tag fiducial marker atvarious blur scales}
\begin{tabularx}{\textwidth}{|Y|Y|Y|}
\cline{1-3}
\tiny{Blur} & \multicolumn{2}{c|}{\tiny{Recognition Rate}} \\\cline{2-3}
 \tiny{Scale}& \tiny{AR Tag} &	\tiny{Pi-Tag} \\ \cline{1-3}
\tiny{15} & \tiny{100} & \tiny{100} \\ \cline{1-3}
\tiny{30} & \tiny{0} & \tiny{100} \\  \cline{1-3}
\tiny{35} & \tiny{0} & \tiny{19} \\ \cline{1-3}
\tiny{50} & \tiny{0} & \tiny{0} \\ \cline{1-3}
\end{tabularx}
\end{minipage}
\label{fig:artag_pitag}
\captionof{figure}{Figure showing ARTag and Pi-tag blurred with various blur
scales at different orientation. Table on the right shows the recognition rate
(in percent) of both fiducial markers at various blur scales along all blur
orientations.  Recognition rates for both tag is significantly reduces due to blur.
For severe blur, detection is not possible.}
\end{minipage}

@@

[MSB: You have to describe the algorithm here as discussed yesterday.  Please complete this
part.]
 We give a brief overview of our algorithm here and details to each step in the following. Figure \ref{fig:overall_flow} shows the process involved in fiducial detection
process. Our detection algorithm has four steps.  First, we apply a Gabor filter on the camera frame, next . . .

@@

Figure \ref{fig:overall_flow} shows the process involved in fiducial detection
process.

\begin{figure}
\includegraphics[width=\linewidth]{overall_flow.pdf}
\caption{Overall Workflow - [MSB: Details?  This is why I said this I didn't think this
was the updated version of the paper. We discussed this yesterday, you need details in all of your captions.] }
\label{fig:overall_flow}
\end{figure}

\noindent\textbf{Gabor filter}: A 2D Gabor filter is a Gaussian kernel function
modulated by a sinusoidal plane wave. It is used to find high gradient patches from the
image. In our case, it will detect blur invariant sections of the fiducials. We
have applied Gabor filter for eight different orientations ($\theta = 0, 45,
90, 135, 180, 225, 270, 315$). We have used following parameters for
creating each Gabor kernel: $\lambda = 8$, $\gamma = 0.5$, $\sigma =
0.56\lambda$, $\psi = 0 \text{(for real part)}, \pi/2 \text{(for imaginary
part)}$.
Then L2 norm of outputs along all orientations is calculated and finally L2
normed image is binarized.

@@

\begin{figure}[h!]
\centering
  \includegraphics[width=\linewidth]{training_data.pdf}
  \caption{Training data for the fiducial pattern with binary code ``01''}
  \label{fig:training_data}
\end{figure}

@@

[MSB: As discussed yesterday, in the table reporting the results you need to give the 
number of frames in tested video clip.  We may also need to comment on the
number of dropped frames if this is possible to get. We mentioned this in the
paper, but never mentioned this in the experimetal results.]

@@

\begin{figure}
\begin{subfigure}{0.5\textwidth}
\centering
  \includegraphics[width=\linewidth]{output_00.jpg}
  \caption{Binary code ``00''}
  \label{fig:output0}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
\centering
  \includegraphics[width=\linewidth]{output_01.jpg}
  \caption{Binary code ``01''}
  \label{fig:output1}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
\centering
  \includegraphics[width=\linewidth]{output_10.jpg}
  \caption{Binary code ``10''}
  \label{fig:output2}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
\centering
  \includegraphics[width=\linewidth]{output_11.jpg}
  \caption{Binary code ``11''}
  \label{fig:output3}
  \end{subfigure}
  \caption{Sample Outputs for two bit binary coded fiducials}
\end{figure}

Our system has also been tested on images containing multiple fiducial patterns
in the same frame. Our algorithm successfully detected all fiducial patterns as
well as correctly classified them as shown in Figure \ref{fig:output_all}.
\begin{figure}
\centering
  \includegraphics[width=.8\linewidth]{output_all_2.jpg}
  \caption{Sample output containing all two bit binary coded fiducial patterns}
  \label{fig:output_all}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{recognition_rate.png}
\caption{Comparison of recognition rate of AR Tag and our fiducials on
blur simulated data at various blur scales. It can be clearly seen that except
fiducial with binary code ``00'', our fiducial patterns are
recognised all times.}
\label{fig:recognition_rate}
\end{figure}

@@

\begin{table}
\caption{Comparison of recognition rate of AR Tag and our fiducials on real
data captured through AR Drone. Each row shows analysis of a test
dataset captured for our fiducial with different binary code embedded in it}
\centering
\begin{tabularx}{0.8\textwidth}{|Y|Y|Y|Y|}
\cline{1-4}
\multirow{2}{*}{Test Dataset ID} & \multirow{2}{*}{Binary Code}
&\multicolumn{2}{c|}{Recognition Rate (\%)} \\ \cline{3-4}
& & Our Fiducial & AR Tag\\\cline{1-4}
1 & 00 & 86.5 &  65.6 \\ \cline{1-4}
2 & 01 & 94.1 &  61.9 \\ \cline{1-4}
3 & 10 & 92.74 & 62.4 \\ \cline{1-4}
4 & 11 & 93.54 & 60.3 \\ \cline{1-4}
\end{tabularx}
\label{tab:recongition_accuracy}
\end{table}

@@

We have used sample image sequence (consisting of 20 frames [MSB: This is inviting trouble, I can guarentee you this will likely get your paper rejected.]) to test the performance of BLUT\cite{Wu:2011} and compare it with our result on the same
image sequence. From Figure \ref{fig:BLUT_output}, it can be inferred that BLUT
is able to track the fiducial when the position of fiducial does not change too
much in successive frames. Also, it can be seen that, once BLUT looses the
track of the fiducial, it is not able to recover from that. But, our algorithm
is able to track the fiducial irrespective of the change in the position of the
fiducial in the image as shown in Figure \ref{fig:our_output}.

\begin{figure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{11.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{12.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{13.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{14.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{15.jpg}
\end{subfigure}
\caption{Output of BLUT on sample image sequence. It can be seen that from third
frame, BLUT looses the track of our fiducial}
\label{fig:BLUT_output}
\end{figure}

\begin{figure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{output11.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{output12.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{output13.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{output14.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{output15.jpg}
\end{subfigure}
\caption{Output of our algorithm on image sequence used in
Figure \ref{fig:BLUT_output}. Our algorithm is able to detect our fiducial in
all frames.}
\label{fig:our_output}
\end{figure}

>>>>

In order to be effective, fiducial markers (or simply, fiducials) need
to be easily detected in the scene.  A variety of fiducial markers
have been proposed in the literature (e.g.~\cite{NaimarkF02,ARToolkit02,Fiala05,Pitag13,runetag11}).
These take the form of binary codes arranged into rectangular grids (\cite{ARToolkit02,Fiala05})
or other geometric features arranged in predefined spatial patterns
(\cite{NaimarkF02,Pitag13,runetag11}).
Figure \ref{fig:teaser}-top shows an example of the popular ARTag\cite{Fiala05} as
seen from a quadcopter.  A problem for existing fiducials is  that low-cost quadcopters
often exhibit very quick and erratic physical movements that
results in motion blur in the quadcopters onboard camera.  This motion blur has
an adverse effect the  recognition of fiducial  markers.  This can be seen in
Figure \ref{fig:teaser}(top) where the ARTag cannot be recognized due to motion
blur. This is not too surprising as most  existing fiducials are not explicitly
designed to handle motion blur.

@@

@@

Most tracking methods( \cite{Ross:2008,Wu:2009,Perez02,Mei:2009} ) assume the
image sequence to be blur free. In reality, however, motion blur in video
sequences is often unavoidable. Wu et al.\cite{Wu:2011} have developed
BLUr-driven Tracker (BLUT) framework for tracking motion-blurred targets. BLUT
is based on the observation that although motion blurs degrade the visual
features of the target, they at the same time, provide useful cues about the
movements to help tracking.

@@

Before we detail the design of our fiducial, we examine the performance of two
popular fiducials under motion blur.  Specifically we examine ARTags
\cite{Fiala05} and PiTags\cite{Pitag13} given their difference in geometry design.

To simulate the appearance of the maker as seen by a quadcopter,  we scaled down
ARTag as well as PiTag fiducial to size 150x150. Both fiducials are then blurred
at various orientations with different blurs scales (denoted in pixels).   The
blur motion ranged from 15 to 50 in magnitude, representing small to significant
motion blur. Figure \ref{fig:artag_pitag} shows the visual appearance of the
blurred tags. We then use try to detect the markers using the ALVAR
library\cite{alvar} and Pi-Tag library\cite{ros_pitag}.
The table in the left side of Figure
\ref{fig:artag_pitag} shows the recognition rate (in percent) of two fiducial
markers at various blur scales under different orientation.   As we can see,
the PiTag performance quickly diminished under small amounts of blur, however,
at 35 motion blur, ARTag is recognition rate drops to less than 20\%.

\noindent\begin{minipage}[h!]{\textwidth}
\noindent\begin{minipage}{0.6\textwidth}
\includegraphics[width=\textwidth]{artag_pitag.pdf}
%\captionof{figure}{Blurred AR Tag and Pi--tag with various blur scales}
\end{minipage}
\begin{minipage}{0.35\textwidth}
%\captionof{table}{Recognition rate of AR Tag and Pi-tag fiducial marker atvarious blur scales}
\begin{tabularx}{\textwidth}{|Y|Y|Y|}
\cline{1-3}
\small{Blur} & \multicolumn{2}{c|}{ \small{Recognition Rate}}
\\\cline{2-3}
\small{Scale}& \small{AR Tag} &	\small{Pi-Tag} \\ \cline{1-3}
\small{15} & \small{100} & \small{100} \\ %\cline{1-3}
\small{30} & \small{0} & \small{100} \\  %\cline{1-3}
\small{35} & \small{0} & \small{19} \\ %\cline{1-3}
\small{50} & \small{0} & \small{0} \\ \cline{1-3}
\end{tabularx}
\end{minipage}
\label{fig:artag_pitag}
\captionof{figure}{Figure showing ARTag and Pi-tag blurred with various blur
scales at different orientation. Table on the right shows the recognition rate
(in percent) of both fiducial markers at various blur scales along all blur
orientations.  Recognition rates for both tag is significantly reduces due to blur.
For severe blur, detection is not possible.}
\end{minipage}

@@

We give a brief overview of our algorithm here and details to each step in the
following. Figure \ref{fig:overall_flow} shows the process involved in fiducial
detection process. Our detection algorithm has four steps. First, we apply a
Gabor filter (Step 1) on the image captured through AR Drone. Next, we find the
clusters of patches found in Gabor output using hierarchical clustering (Step
2). Later, we perform Principal Component Analysis (PCA) on each cluster, to
find the blur invariant direction (Step 3). The intensity profile along this
direction is found in the original image. And finally, we match this intensity
profile with training data using K-Nearest neighbor classifier (Step 4).

@@

\begin{figure}[ht!]
\includegraphics[width=\linewidth]{overall_flow.pdf}
\caption{The flow of our algorithm to detect and classify fiducial in the scene
captured from AR Drone. Four step process includes Gabor Filter(Step 1),
Hierarchical Clustering (Step 2), PCA (Step 3) and Classification using
K-Nearest Neighbor (KNN) classifier (Step 4). Training data for KNN classifier is gathered
offline.}
\label{fig:overall_flow}
\end{figure}

\noindent Details of each of the steps are as follows:\\
\noindent\textbf{Gabor filter}: A 2D Gabor filter is a Gaussian kernel function
modulated by a sinusoidal plane wave. It is used to find high gradient patches from the
image. In our case, it will detect blur invariant sections of the fiducials. We
have applied Gabor filter for eight different orientations ($\theta = 0, 45,
90, 135, 180, 225, 270, 315$). We have used following parameters for
creating each Gabor kernel: $\lambda = 8$, $\gamma = 0.5$, $\sigma =
0.56\lambda$, $\psi = 0 \text{(for real part)}, \pi/2 \text{(for imaginary
part)}$.
Then L2 norm of outputs along all orientations is calculated and finally L2
normed image is binarized.

@@

\begin{figure}[h!]
\centering
  \includegraphics[width=\linewidth]{training_data.pdf}
  \caption{Process to create training data for the fiducial pattern with binary
  code ``01''. Synthetic pattern is blurred along various orientations. Gabor
  filter is applied on the blurred pattern. Intensity profile is found along the
  first principal component of the clustered Gabor output. Same process is used
  to create training data for other fiducial patterns.}
  \label{fig:training_data}
\end{figure}

@@

@@

\begin{figure}[hb!]
\begin{subfigure}{0.5\textwidth}
\centering
  \includegraphics[width=\linewidth]{output_00.jpg}
  \caption{Binary code ``00''}
  \label{fig:output0}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
\centering
  \includegraphics[width=\linewidth]{output_01.jpg}
  \caption{Binary code ``01''}
  \label{fig:output1}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
\centering
  \includegraphics[width=\linewidth]{output_10.jpg}
  \caption{Binary code ``10''}
  \label{fig:output2}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
\centering
  \includegraphics[width=\linewidth]{output_11.jpg}
  \caption{Binary code ``11''}
  \label{fig:output3}
  \end{subfigure}
  \caption{Sample outputs for two bit binary coded fiducials. Class label
  attached to the detected fiducial is decimal equivalent of the binary code of
  the detected fiducial.}
\end{figure}

Our system has also been tested on images containing multiple fiducial patterns
in the same frame. Our algorithm successfully detected all fiducial patterns as
well as correctly classified them as shown in Figure \ref{fig:output_all}.

\begin{figure}
\centering
  \includegraphics[width=.8\linewidth]{output_all_2.jpg}
  \caption{Sample output containing all two bit binary coded fiducial patterns
  in single frame.}
  \label{fig:output_all}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\linewidth]{recognition_rate.png}
\caption{Comparison of recognition rate of AR Tag and our fiducials on
blur simulated data at various blur scales. It can be clearly seen that except
fiducial with binary code ``00'', our fiducial patterns are
recognised all times.}
\label{fig:recognition_rate}
\end{figure}

@@

\begin{table}[h!]
\caption{Comparison of recognition rate of AR Tag and our fiducials on real
data captured through AR Drone. Each row shows analysis of a test
dataset captured for our fiducial with different binary code embedded in it.
Each dataset has around 1000 frames captured in around two minutes.}
\centering
\begin{tabularx}{\textwidth}{|c|Y|Y|Y|Y|}
\cline{1-5}
\multirow{2}{*}{Test \#} & \multirow{2}{*}{Number of Frames}
&\multirow{2}{*}{Binary Code} &\multicolumn{2}{c|}{Recognition Rate (\%)} \\
\cline{4-5} & & & Our Fiducial & AR Tag\\\cline{1-5}
1 & 1205 & 00 & 86.5 &  65.6 \\ \cline{1-5}
2 & 1047 & 01 & 94.1 &  61.9 \\ \cline{1-5}
3 & 1102 & 10 &  92.74 & 62.4 \\ \cline{1-5}
4 & 1081 & 11 & 93.54 & 60.3 \\ \cline{1-5}
\end{tabularx}
\label{tab:recongition_accuracy}
\end{table}

@@

We have used four image sequences (consisting of around 1000 frames each) , each
one containing our different fiducial pattern, to test the performance of
BLUT\cite{Wu:2011} and compare it with our result on the same image sequence.
From top rows of Figure \ref{fig:BLUT_compare_00}-\ref{fig:BLUT_compare_11}, it
can be inferred that BLUT is able to track the fiducial when the position of
fiducial does not change too much in successive frames. Also, it can be seen
that, once BLUT looses the track of the fiducial, it is not able to recover
from that. But, our algorithm is able to track the fiducial irrespective of the
change in the position of the fiducial in the image as shown in bottom rows of Figure
\ref{fig:BLUT_compare_00}-\ref{fig:BLUT_compare_11}.

We have also found that, even if we reset the BLUT tracker after loosing track,
it looses track again after around 100 frames i.e., approximately 6 seconds.
When we checked the timestamp data from image header captured through AR Drone,
we found that, there was difference of 0.14 seconds between two successive
frames in the earlier case, which clearly suggests the dropping of frame. Also,
there were around 50 instances in 1000 frames where timestamp difference between two
successive frames was greater than 0.1 seconds. So, it is evident that
due to dropping of frames combined with unstable motion of quadcopter, tracking
through quadcopter using conventional tracking methods is not accurate.

\begin{figure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_00/2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_00/3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_00/4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_00/5.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_00/6.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_00/output2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_00/output3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_00/output4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_00/output5.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_00/output6.jpg}
\end{subfigure}
\caption{Top: Output of BLUT\cite{Wu:2011} on sample image sequence containing ``00''
binary coded fiducial, Bottom: Output of our algorithm on the same image
sequence. BLUT is able to track the fiducial till third frame, but from fourth
frame, BLUT looses track of the fiducial. In first three frames, size of the
fiducials is less but in fourth and fifth frame it is bigger, hinting sudden
forward movement of quadcopter.}
\label{fig:BLUT_compare_00}
\end{figure}

\begin{figure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_01/11.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_01/12.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_01/13.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_01/14.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_01/15.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_01/output11.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_01/output12.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_01/output13.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_01/output14.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_01/output15.jpg}
\end{subfigure}
\caption{Top: Output of BLUT\cite{Wu:2011} on sample image sequence containing
``01'' binary coded fiducial, Bottom: Output of our algorithm on the same image
sequence. BLUT looses the track from third frame.}
\label{fig:BLUT_compare_01}
\end{figure}

\begin{figure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_10/1.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_10/2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_10/3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_10/4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_10/5.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_10/output1.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_10/output2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_10/output3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_10/output4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_10/output5.jpg}
\end{subfigure}
\caption{Top: Output of BLUT\cite{Wu:2011} on sample image sequence containing
``10'' binary coded fiducial, Bottom: Output of our algorithm on the same image
sequence. From second frame itself, BLUT looses the track.}
\label{fig:BLUT_compare_10}
\end{figure}

\begin{figure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_11/2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_11/3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_11/4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_11/5.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_11/6.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_11/output2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_11/output3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_11/output4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_11/output5.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_11/output6.jpg}
\end{subfigure}
\caption{Top: Output of BLUT\cite{Wu:2011} on sample image sequence containing
``11'' binary coded fiducial, Bottom: Output of our algorithm on the same image
sequence. BlUT lost the track from third frame. There is sudden reversal of
direction of quadcopter from third frame. In first two frames quadcopter was
going up, but suddenly it moved down in third frame.}
\label{fig:BLUT_compare_11}
\end{figure}
